---
title: "Assignment_2"
author: "Barbiero Lorenzo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


##Exercise 1 - Discrete random variable

pdf and cdf

```{r}
k <- c(1:5)
ddisc <- k/15
pdisc <- cumsum(ddisc)
```

Plot pdf
```{r}
pdfplt <- data.frame(k,ddisc)

(g <- ggplot(pdfplt, aes(x=k,y=ddisc)))+geom_bar(stat="identity", width=1,fill="dodgerblue", color="ivory")
```

plot cdf

```{r}
cdfplt <- data.frame(k,pdisc)

(g <- ggplot(cdfplt, aes(x=k,y=pdisc)))+geom_bar(stat="identity", width=1, fill = "coral1", color="ivory")
```
Compute mean and variance

```{r}
E_x <- sum(k * ddisc)
E_x2 <- sum(k * k * ddisc)
var <- E_x2 - (E_x)**2 

E_x
var
```

Compute E[k(6-k)]

E[k(6-k)]=E[6^k-k^2]=6 E[k] - E[k^2]
```{r}
E_k = 6*E_x - E_x2
E_k
```

Draw random samples from distribution

```{r}
rdisc = function(n) {
  x <- runif(n,0,1)
  y <- ifelse(x < 1/15, 1,
              ifelse(x < 3/15, 2,
                     ifelse(x < 6/15, 3,
                            ifelse(x < 10/15, 4, 5))))
  
}

sampler <- data.frame(rdisc(10e+4))
colnames(sampler) <- "samples"

(g <- ggplot(sampler) + 
   geom_histogram(binwidth=1 ,fill = "deeppink3", color="white",aes(x=samples, y=after_stat(density))) +
   geom_point(data = pdfplt, size=7, color = "dodgerblue", aes(x=k, y=ddisc)))
```

##Exercise 2 - Random continuos variable

Define pdf and cdf

```{r}


x <- seq(0,5,0.05)
a <- 1
b <- 4
c <- 2

pdf <- ifelse(x<a | x>b, 0, ifelse(x<c, 2*(x-a)/((b-a)*(c-a)), 2*(b-x)/((b-a)*(b-c))))
cdf <- ifelse(x<a, 0,
              ifelse(x<c,(x-a)**2/((b-a)*(c-a)),
                     ifelse(x<b,(c-a)/(b-a)+(2*b*(x-c)-x**2+c**2)/((b-c)*(b-a)),1)))

X <- data.frame(x,pdf,cdf)
```

Plot pdf
```{r}
p <- ggplot(X, aes(x=x,y=pdf)) +
     geom_line(lwd=1, color = "dodgerblue")
p
```

Plot cdf
```{r}
p <- ggplot(X, aes(x=x,y=cdf)) +
     geom_line(lwd=1, color = "coral1")
p
```

Sample from the pdf using the accept/reject method.

```{r}
samplefunc <- function(N) {
  i <- 1
  SMPL <- rep(0,N)
  while (i<N+1) {
    x <- runif(1,a,b)
    y <- runif(1,0,1)
    if(x<=c) {
      if (y < 2*(x-a)/((b-a)*(c-a))) {
        SMPL[i] <- x
        i <- i+1
      }
    }
    if(x>c) {
      if (y < 2*(b-x)/((b-a)*(b-c))) {
        SMPL[i] <- x
        i <- i+1
      }
    }
  }
  return(SMPL)
}
```

```{r}
Y <- data.frame(samplefunc(1e+4))
colnames(Y) <- "samples"

(g <- ggplot(Y) + 
   geom_histogram(fill = "deeppink3", color="white",aes(x=samples, y=after_stat(density))) +
   geom_line(data = X, lwd=1, color = "dodgerblue", aes(x=x, y=pdf)))
```

##Exercise 3 - Waiting time at the Doctor

Simulated waiting times for 60 people, showing expected and computed mean waiting time

```{r}
X <- data.frame(rexp(60,1/30))
colnames(X) <- "wait_time"
wt <- mean(X$wait_time)

(g <- ggplot(X, aes(x=wait_time)) + geom_histogram(binwidth= 5, fill = "deeppink3", color="white"))
```
Probability of waiting less than 12 minutes

```{r}
wt <- pexp(12,1/30)
wt
```
Probability of waiting more than 1hr

```{r}
wt <- 1 - pexp(60,1/30)
wt
```

##Exercise 4 - Multiple choices exam

This is a standard application of the Bayes theorem, where:
- R = "right answer"
- K = "knows the answer"
We have P(K) = 0.7, P(R|not(K)) = 0.2 (so P(not(R)|not(K))=0.8), P(K|R) = ? from the text,
we also reasonably assume P(R|K) = 1, and P(not(R)|K)=0

After some algebraic manipulation we get to

P(K|R) = [P(R|K)P(K)]/[P(R|K)P(K)+P(R|not(K))P(not(K))]

```{r}
a <- (1*0.7)/(1*0.7+0.2*0.3)
a
```


##Exercise 5 - Train waiting time

The first train will leave at 11:00, the next ones would be at 11:30 and 12:00.
For time invariance I will draw numbers from 0 (10:45) to 60 (11:45) with train times marked as 15,45,75.

```{r}
N <- 100000
t <- runif(N,0,60)
wait <- ifelse(t<15,15-t,ifelse(t<45,45-t,75-t))

Y <- data.frame(wait)
colnames(Y) <- "wait_times"

(g <- ggplot(Y, aes(x=wait_times)) + geom_histogram(binwidth=1,fill = "deeppink3", color="white", aes(y=after_stat(density))))
```

Wait at most ten minutes
```{r}
wt <- length(which(Y$wait_times<=10))/length(Y$wait_times)
wt
```

Wait at least 15 minutes
```{r}
wt <- length(which(Y$wait_times>15))/length(Y$wait_times)
wt
```

Average waiting time
```{r}
wt <- mean(Y$wait_times)
wt
```

##Exercise 6 - Stock Investment
The return on the investment follows a normal distribution.
Starting investment is 200*85=17000€ so a profit of 800€ translates to a profit of 4.7%.
The solution is easily obtained through the normal cdf

```{r}
target_perc <- 800/170
prob <- 1 - pnorm(target_perc,10,12)
prob
```

